Causal inference is not a statistical problem

### 2023-04-04 manuscript.qmd
update R pacakge

The data generated to create the figures displayed here are included in an R package titled `causalquartet`.

@@

```{r}
#| eval: false
#| echo: true
library(tidyverse)
# devtools::install_github("LucyMcGowan/causalquartet")
library(causalquartet)

@@

ggplot(causalquartet, aes(x = x, y = y)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = "y ~ x") +
  facet_wrap(~type)

@@

causalquartet %>%
  nest_by(type) %>%
  mutate(`Y ~ X` = round(coef(lm(y ~ x, data = data))[2], 2),
         `Y ~ X + Z` = round(coef(lm(y ~ x + z, data = data))[2], 2),
         `Correlation of X and Z` = round(cor(data$x, data$z), 2)) %>%
  select(-data, `Data generating mechanism` = type) %>%
  knitr::kable()
```

>>>>

The data generated to create the figures displayed here are included in an R package titled `quartet`.

@@

```{r}
#| eval: false
#| echo: true
library(tidyverse)
# devtools::install_github("LucyMcGowan/quartet")
library(quartet)

@@

ggplot(causal_quartet, aes(x = x, y = y)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = "y ~ x") +
  facet_wrap(~dataset)

@@

causal_quartet %>%
  nest_by(dataset) %>%
  mutate(`Y ~ X` = round(coef(lm(y ~ x, data = data))[2], 2),
         `Y ~ X + Z` = round(coef(lm(y ~ x + z, data = data))[2], 2),
         `Correlation of X and Z` = round(cor(data$x, data$z), 2)) %>%
  select(-data, `Data generating mechanism` = dataset) %>%
  knitr::kable()
```
